A Hitchhiker's Guide to Reproducible Research" # replace with something serious

### 2021-05-04 manuscript.Rmd
small changes after reading

Another advantage of Markdown is that you can easily version-control it with Git.
You may be familiar with Microsoft Words' "Track Changes"-Feature and version control is similar in their basic idea but more potent in their features.
Instead of tracking only one file, you can keep track of the whole project directory, and instead of losing all changes when you agree to them, the entire history is preserved transparently.
For example, this paper has been going through `r length(git2r::commits())` `r link("https://github.com/aaronpeikert/repro-tutorial/commits/master", "iterations")`.
To activate Git in a given project, you can call:
<!-- Hands-on: Introduce Git -->

@@

@@

Pull requests allow anyone to contribute to a project, even though they do not have write access, while the authors still retain all control.
If someone wants to contribute, but they have no permission to write to a repository, they can create a copy of the project, called "fork", where they can push their changes.
They then request that you (or anyone with write permissions) "pull" these changes.
Any new pull request can be seen on GitHub:

@@

Before you incorporate changes from someone else, you can review and change them.
This review step can also be useful for collaboration, because you can invite a collaborator to take a look at changes you want to do.
It is therefore sometimes useful to create a pull request even though you have permission to push, because it invites your collaborators to comment or change your proposal.

>>>>

Another advantage of Markdown is that you can easily version-control it with Git.
You may be familiar with Microsoft Words' "Track Changes"-Feature.
Version control is similar in its basic idea but more potent in its features.
Instead of tracking only one file, you can keep track of the whole project directory, and instead of losing all changes when you agree to them, the entire history is preserved transparently.
For example, this paper has been going through `r length(git2r::commits())` `r link("https://github.com/aaronpeikert/repro-tutorial/commits/master", "iterations")`.
To activate Git in a given project, you can call:
<!-- Hands-on: Introduce Git -->

@@

You see the linkage in Figure \@ref(fig:issue).

@@

Pull requests allow anyone to contribute to a project, even though they do not have write access, while the authors still retain all control.
If someone wants to contribute, but they have no permission to write to a repository, they can create a copy of the project, called "fork", where they can push their changes.
For example if you found an error in this manuscript, you can not simply change it, because you have no write access.
However, you can create a fork in your account, where you have write permission:

``` r
usethis::create_from_github("aaronpeikert/repro-tutorial", fork = TRUE)
```
In this copy you then make any changes you want.
You could then request that we (or anyone with write permissions) "pull" these changes.
You can view new pull request for any project with:

@@

Before incorporating changes from someone else, they can be reviewed and adepted.
This review step can also be useful for collaboration, because you can invite a collaborator to take a look at changes you want to do.
It is therefore sometimes useful to create a pull request even though you have permission to push, because it invites your collaborators to comment or change your proposal.
